---
title: "Untitled"
author: "Kwame Forbes"
date: "9/19/2022"
output: html_document
---
Comparing Pengda WTvMUT vs ELife

Dependencies
```{r}
library(tidyr)
library(pheatmap)
library(BioVenn)
library(ggplot2)
library(ggpubr)
library(org.Hs.eg.db)
library("AnnotationHub")
library(GO.db)
library(dplyr)
```

```{r}
IncLevelDifference.variable = 0.05
FDR.variable = 0.05
coverage = 100
psidiff = 0.1
elifeFDR = 0.25
elifeSeedScore = 3


f <- function(x, ...) {
  abs(max(x) -min(x))
}
```


This is all AS events for Pengda WT vs T200M that's has 50 plus counts
```{r}

#RI Filtering----
WTvT200M_ri_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvT200M/BAM/RI.MATS.JC.txt",header = T)
WTvT200M_ri_jc <- as.data.frame(WTvT200M_ri_jc)

AS = as.data.frame(rep("RI",dim(WTvT200M_ri_jc)[1]))
names(AS)[names(AS) == 'rep("RI", dim(WTvT200M_ri_jc)[1])'] <- "events"
WTvT200M_ri_jc = cbind(WTvT200M_ri_jc,AS)
Comparison = as.data.frame(rep("WTvT200M",dim(WTvT200M_ri_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvT200M", dim(WTvT200M_ri_jc)[1])'] <- "Comparison"
WTvT200M_ri_jc = cbind(WTvT200M_ri_jc,Comparison)

WTvT200M_ri_jc = unite(WTvT200M_ri_jc,"Position",c(4:11),sep = ":",remove = T)
WTvT200M_ri_jc$EVENT <- paste(WTvT200M_ri_jc$geneSymbol,WTvT200M_ri_jc$Position,sep = "_")
rownames(WTvT200M_ri_jc) <- WTvT200M_ri_jc$EVENT
WTvT200M_ri_jc <- subset(WTvT200M_ri_jc, select = -c(1:5))

WTvT200M_ri_jc <- separate(WTvT200M_ri_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_ri_jc <- separate(WTvT200M_ri_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_ri_jc <- separate(WTvT200M_ri_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_T200M1","IJC_SAMPLE_T200M2","IJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_ri_jc <- separate(WTvT200M_ri_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_T200M1","SJC_SAMPLE_T200M2","SJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_ri_jc[1:12] <- as.numeric(unlist(WTvT200M_ri_jc[1:12]))

WTvT200M_ri_jc <- separate(WTvT200M_ri_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvT200M_ri_jc <- separate(WTvT200M_ri_jc, col = IncLevel2, into = c("IncLevel_T200M1","IncLevel_T200M2","IncLevel_T200M3"),sep = ",",remove = T)
WTvT200M_ri_jc[17:22] <- as.numeric(unlist(WTvT200M_ri_jc[17:22]))
WTvT200M_ri_jc <- na.omit(WTvT200M_ri_jc)

WTvT200M_ri_jc <- subset(WTvT200M_ri_jc,
                         apply(WTvT200M_ri_jc[c(1,4)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_ri_jc[c(2,5)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_ri_jc[c(3,6)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_ri_jc[c(7,10)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_ri_jc[c(8,11)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_ri_jc[c(9,12)], MARGIN =  1,mean)>=coverage)

#WTvT200M_ri_jc_filtered = subset(WTvT200M_ri_jc,FDR <= FDR.variable&abs(IncLevelDifference)>=IncLevelDifference.variable)


#SE Filtering----
WTvT200M_se_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvT200M/BAM/SE.MATS.JC.txt",header = T)
WTvT200M_se_jc <- as.data.frame(WTvT200M_se_jc)

AS = as.data.frame(rep("SE",dim(WTvT200M_se_jc)[1]))
names(AS)[names(AS) == 'rep("SE", dim(WTvT200M_se_jc)[1])'] <- "events"
WTvT200M_se_jc = cbind(WTvT200M_se_jc,AS)
Comparison = as.data.frame(rep("WTvT200M",dim(WTvT200M_se_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvT200M", dim(WTvT200M_se_jc)[1])'] <- "Comparison"
WTvT200M_se_jc = cbind(WTvT200M_se_jc,Comparison)

WTvT200M_se_jc = unite(WTvT200M_se_jc,"Position",c(4:11),sep = ":",remove = T)
WTvT200M_se_jc$EVENT <- paste(WTvT200M_se_jc$geneSymbol,WTvT200M_se_jc$Position,sep = "_")
rownames(WTvT200M_se_jc) <- WTvT200M_se_jc$EVENT
WTvT200M_se_jc <- subset(WTvT200M_se_jc, select = -c(1:5))

WTvT200M_se_jc <- separate(WTvT200M_se_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_se_jc <- separate(WTvT200M_se_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_se_jc <- separate(WTvT200M_se_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_T200M1","IJC_SAMPLE_T200M2","IJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_se_jc <- separate(WTvT200M_se_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_T200M1","SJC_SAMPLE_T200M2","SJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_se_jc[1:12] <- as.numeric(unlist(WTvT200M_se_jc[1:12]))

WTvT200M_se_jc <- separate(WTvT200M_se_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvT200M_se_jc <- separate(WTvT200M_se_jc, col = IncLevel2, into = c("IncLevel_T200M1","IncLevel_T200M2","IncLevel_T200M3"),sep = ",",remove = T)
WTvT200M_se_jc[17:22] <- as.numeric(unlist(WTvT200M_se_jc[17:22]))
WTvT200M_se_jc <- na.omit(WTvT200M_se_jc)

WTvT200M_se_jc <- subset(WTvT200M_se_jc,
                         apply(WTvT200M_se_jc[c(1,4)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_se_jc[c(2,5)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_se_jc[c(3,6)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_se_jc[c(7,10)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_se_jc[c(8,11)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_se_jc[c(9,12)], MARGIN =  1,mean)>=coverage)


#WTvT200M_se_jc_filtered = subset(WTvT200M_se_jc,FDR <= FDR.variable&abs(IncLevelDifference)>=IncLevelDifference.variable)

#A3SS Filtering----
WTvT200M_a3ss_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvT200M/BAM/A3SS.MATS.JC.txt",header = T)
WTvT200M_a3ss_jc <- as.data.frame(WTvT200M_a3ss_jc)

AS = as.data.frame(rep("A3SS",dim(WTvT200M_a3ss_jc)[1]))
names(AS)[names(AS) == 'rep("A3SS", dim(WTvT200M_a3ss_jc)[1])'] <- "events"
WTvT200M_a3ss_jc = cbind(WTvT200M_a3ss_jc,AS)
Comparison = as.data.frame(rep("WTvT200M",dim(WTvT200M_a3ss_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvT200M", dim(WTvT200M_a3ss_jc)[1])'] <- "Comparison"
WTvT200M_a3ss_jc = cbind(WTvT200M_a3ss_jc,Comparison)

WTvT200M_a3ss_jc = unite(WTvT200M_a3ss_jc,"Position",c(4:11),sep = ":",remove = T)
WTvT200M_a3ss_jc$EVENT <- paste(WTvT200M_a3ss_jc$geneSymbol,WTvT200M_a3ss_jc$Position,sep = "_")
rownames(WTvT200M_a3ss_jc) <- WTvT200M_a3ss_jc$EVENT
WTvT200M_a3ss_jc <- subset(WTvT200M_a3ss_jc, select = -c(1:5))

WTvT200M_a3ss_jc <- separate(WTvT200M_a3ss_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_a3ss_jc <- separate(WTvT200M_a3ss_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_a3ss_jc <- separate(WTvT200M_a3ss_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_T200M1","IJC_SAMPLE_T200M2","IJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_a3ss_jc <- separate(WTvT200M_a3ss_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_T200M1","SJC_SAMPLE_T200M2","SJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_a3ss_jc[1:12] <- as.numeric(unlist(WTvT200M_a3ss_jc[1:12]))

WTvT200M_a3ss_jc <- separate(WTvT200M_a3ss_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvT200M_a3ss_jc <- separate(WTvT200M_a3ss_jc, col = IncLevel2, into = c("IncLevel_T200M1","IncLevel_T200M2","IncLevel_T200M3"),sep = ",",remove = T)
WTvT200M_a3ss_jc[17:22] <- as.numeric(unlist(WTvT200M_a3ss_jc[17:22]))
WTvT200M_a3ss_jc <- na.omit(WTvT200M_a3ss_jc)

WTvT200M_a3ss_jc <- subset(WTvT200M_a3ss_jc,
                         apply(WTvT200M_a3ss_jc[c(1,4)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_a3ss_jc[c(2,5)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_a3ss_jc[c(3,6)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_a3ss_jc[c(7,10)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_a3ss_jc[c(8,11)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_a3ss_jc[c(9,12)], MARGIN =  1,mean)>=coverage)

#WTvT200M_a3ss_jc_filtered = subset(WTvT200M_a3ss_jc,FDR <= FDR.variable&abs(IncLevelDifference)>=IncLevelDifference.variable)

#A5SS Filtering----
WTvT200M_a5ss_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvT200M/BAM/A5SS.MATS.JC.txt",header = T)
WTvT200M_a5ss_jc <- as.data.frame(WTvT200M_a5ss_jc)

AS = as.data.frame(rep("A5SS",dim(WTvT200M_a5ss_jc)[1]))
names(AS)[names(AS) == 'rep("A5SS", dim(WTvT200M_a5ss_jc)[1])'] <- "events"
WTvT200M_a5ss_jc = cbind(WTvT200M_a5ss_jc,AS)
Comparison = as.data.frame(rep("WTvT200M",dim(WTvT200M_a5ss_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvT200M", dim(WTvT200M_a5ss_jc)[1])'] <- "Comparison"
WTvT200M_a5ss_jc = cbind(WTvT200M_a5ss_jc,Comparison)

WTvT200M_a5ss_jc = unite(WTvT200M_a5ss_jc,"Position",c(4:11),sep = ":",remove = T)
WTvT200M_a5ss_jc$EVENT <- paste(WTvT200M_a5ss_jc$geneSymbol,WTvT200M_a5ss_jc$Position,sep = "_")
rownames(WTvT200M_a5ss_jc) <- WTvT200M_a5ss_jc$EVENT
WTvT200M_a5ss_jc <- subset(WTvT200M_a5ss_jc, select = -c(1:5))

WTvT200M_a5ss_jc <- separate(WTvT200M_a5ss_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_a5ss_jc <- separate(WTvT200M_a5ss_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_a5ss_jc <- separate(WTvT200M_a5ss_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_T200M1","IJC_SAMPLE_T200M2","IJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_a5ss_jc <- separate(WTvT200M_a5ss_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_T200M1","SJC_SAMPLE_T200M2","SJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_a5ss_jc[1:12] <- as.numeric(unlist(WTvT200M_a5ss_jc[1:12]))

WTvT200M_a5ss_jc <- separate(WTvT200M_a5ss_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvT200M_a5ss_jc <- separate(WTvT200M_a5ss_jc, col = IncLevel2, into = c("IncLevel_T200M1","IncLevel_T200M2","IncLevel_T200M3"),sep = ",",remove = T)
WTvT200M_a5ss_jc[17:22] <- as.numeric(unlist(WTvT200M_a5ss_jc[17:22]))
WTvT200M_a5ss_jc <- na.omit(WTvT200M_a5ss_jc)

WTvT200M_a5ss_jc <- subset(WTvT200M_a5ss_jc,
                         apply(WTvT200M_a5ss_jc[c(1,4)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_a5ss_jc[c(2,5)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_a5ss_jc[c(3,6)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_a5ss_jc[c(7,10)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_a5ss_jc[c(8,11)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_a5ss_jc[c(9,12)], MARGIN =  1,mean)>=coverage)

#WTvT200M_a5ss_jc_filtered = subset(WTvT200M_a5ss_jc,FDR <= FDR.variable&abs(IncLevelDifference)>=IncLevelDifference.variable)

#MXE Filtering----
WTvT200M_mxe_jc <- read.table("/nas/longleaf/home/kwamek/AS_Pengda/RMATS-WTvT200M/BAM/MXE.MATS.JC.txt",header = T)
WTvT200M_mxe_jc <- as.data.frame(WTvT200M_mxe_jc)

AS = as.data.frame(rep("MXE",dim(WTvT200M_mxe_jc)[1]))
names(AS)[names(AS) == 'rep("MXE", dim(WTvT200M_mxe_jc)[1])'] <- "events"
WTvT200M_mxe_jc = cbind(WTvT200M_mxe_jc,AS)
Comparison = as.data.frame(rep("WTvT200M",dim(WTvT200M_mxe_jc)[1]))
names(Comparison)[names(Comparison) == 'rep("WTvT200M", dim(WTvT200M_mxe_jc)[1])'] <- "Comparison"
WTvT200M_mxe_jc = cbind(WTvT200M_mxe_jc,Comparison)

WTvT200M_mxe_jc = unite(WTvT200M_mxe_jc,"Position",c(4:13),sep = ":",remove = T)
WTvT200M_mxe_jc$EVENT <- paste(WTvT200M_mxe_jc$geneSymbol,WTvT200M_mxe_jc$Position,sep = "_")
rownames(WTvT200M_mxe_jc) <- WTvT200M_mxe_jc$EVENT
WTvT200M_mxe_jc <- subset(WTvT200M_mxe_jc, select = -c(1:5))

WTvT200M_mxe_jc <- separate(WTvT200M_mxe_jc, col = IJC_SAMPLE_1, into = c("IJC_SAMPLE_WT1","IJC_SAMPLE_WT2","IJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_mxe_jc <- separate(WTvT200M_mxe_jc, col = SJC_SAMPLE_1, into = c("SJC_SAMPLE_WT1","SJC_SAMPLE_WT2","SJC_SAMPLE_WT3"),sep = ",",remove = T)
WTvT200M_mxe_jc <- separate(WTvT200M_mxe_jc, col = IJC_SAMPLE_2, into = c("IJC_SAMPLE_T200M1","IJC_SAMPLE_T200M2","IJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_mxe_jc <- separate(WTvT200M_mxe_jc, col = SJC_SAMPLE_2, into = c("SJC_SAMPLE_T200M1","SJC_SAMPLE_T200M2","SJC_SAMPLE_T200M3"),sep = ",",remove = T)
WTvT200M_mxe_jc[1:12] <- as.numeric(unlist(WTvT200M_mxe_jc[1:12]))

WTvT200M_mxe_jc <- separate(WTvT200M_mxe_jc, col = IncLevel1, into = c("IncLevel_WT1","IncLevel_WT2","IncLevel_WT3"),sep = ",",remove = T)
WTvT200M_mxe_jc <- separate(WTvT200M_mxe_jc, col = IncLevel2, into = c("IncLevel_T200M1","IncLevel_T200M2","IncLevel_T200M3"),sep = ",",remove = T)
WTvT200M_mxe_jc[17:22] <- as.numeric(unlist(WTvT200M_mxe_jc[17:22]))
WTvT200M_mxe_jc <- na.omit(WTvT200M_mxe_jc)

WTvT200M_mxe_jc <- subset(WTvT200M_mxe_jc,
                         apply(WTvT200M_mxe_jc[c(1,4)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_mxe_jc[c(2,5)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_mxe_jc[c(3,6)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_mxe_jc[c(7,10)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_mxe_jc[c(8,11)], MARGIN =  1,mean)>=coverage
                         &apply(WTvT200M_mxe_jc[c(9,12)], MARGIN =  1,mean)>=coverage)

#WTvT200M_mxe_jc_filtered = subset(WTvT200M_mxe_jc,FDR <= FDR.variable&abs(IncLevelDifference)>=IncLevelDifference.variable)

#Combine WTvT200M AS events----
pengda_WTvT200M <- rbind(WTvT200M_ri_jc,WTvT200M_se_jc,WTvT200M_a3ss_jc,WTvT200M_a5ss_jc,WTvT200M_mxe_jc)


```




Elife 50+ counts
```{r}
#Load Dataset of nonnormalized PSI with 50+counts ----

elife = read.csv("/nas/longleaf/home/kwamek/CellCycleAS/AS-nonorm-50counts.csv",header = T,sep = ",")
elife = subset(elife,select = c(-1))

#Renaming Columns----
colnames(elife) <- c("Event","EVENT","GENEID","TP_1","TP_2","TP_3","TP_4","TP_5","TP_6","TP_7","TP_8","TP_9","TP_10","TP_11","TP_12","TP_13","TP_14")
```



Finding D
```{r}
overlap_D = merge(pengda_WTvT200M,elife,by="EVENT")
```

Filtering  Pengda WT vs T200M by FDR and Inc LevelDifference
```{r}
pengda_WTvT200M_filtered <- subset(pengda_WTvT200M,FDR <= FDR.variable & abs(IncLevelDifference)>= IncLevelDifference.variable)
write.csv(pengda_WTvT200M_filtered,"WTvsMUT-AS-SigEVENTS.csv")
```


Filtered Elife by FDR and Score
```{r}
#Load Seeds----
Score1 = read.csv("/nas/longleaf/home/kwamek/score1.csv",sep = ",",header = T)
Score1 = subset(Score1,select = c(-1))
names(Score1)[names(Score1) == 'SCORE'] <- 'SEED1'
names(Score1)[names(Score1) == 'FDR'] <- 'FDR1'

Score2 = read.csv("/nas/longleaf/home/kwamek/score2.csv",sep = ",",header = T)
Score2 = subset(Score2,select = c(-1))
names(Score2)[names(Score2) == 'SCORE'] <- 'SEED2'
names(Score2)[names(Score2) == 'FDR'] <- 'FDR2'
names(Score2)[names(Score2) == 'GENE'] <- 'EVENT'

Score3 = read.csv("/nas/longleaf/home/kwamek/score3.csv",sep = ",",header = T)
Score3 = subset(Score3,select = c(-1))
names(Score3)[names(Score3) == 'SCORE'] <- 'SEED3'
names(Score3)[names(Score3) == 'FDR'] <- 'FDR3'

Score4 = read.csv("/nas/longleaf/home/kwamek/score4.csv",sep = ",",header = T)
Score4 = subset(Score4,select = c(-1))
names(Score4)[names(Score4) == 'SCORE'] <- 'SEED4'
names(Score4)[names(Score4) == 'FDR'] <- 'FDR4'

Score5 = read.csv("/nas/longleaf/home/kwamek/score5.csv",sep = ",",header = T)
Score5 = subset(Score5,select = c(-1))
names(Score5)[names(Score5) == 'SCORE'] <- 'SEED5'
names(Score5)[names(Score5) == 'FDR'] <- 'FDR5'

Score6 = read.csv("/nas/longleaf/home/kwamek/score6.csv",sep = ",",header = T)
Score6 = subset(Score6,select = c(-1))
names(Score6)[names(Score6) == 'SCORE'] <- 'SEED6'
names(Score6)[names(Score6) == 'FDR'] <- 'FDR6'

Score7 = read.csv("/nas/longleaf/home/kwamek/score7.csv",sep = ",",header = T)
Score7 = subset(Score7,select = c(-1))
names(Score7)[names(Score7) == 'SCORE'] <- 'SEED7'
names(Score7)[names(Score7) == 'FDR'] <- 'FDR7'

#filter by Seeds by FDR----
Score1 <- subset(Score1, FDR1 <=elifeFDR)
Score2 <- subset(Score2, FDR2 <=elifeFDR)
Score3 <- subset(Score3, FDR3 <=elifeFDR)
Score4 <- subset(Score4, FDR4 <=elifeFDR)
Score5 <- subset(Score5, FDR5 <=elifeFDR)
Score6 <- subset(Score6, FDR6 <=elifeFDR)
Score7 <- subset(Score7, FDR7 <=elifeFDR)

#merge seeds----
BiggerSeed <- merge(Score1,Score2, by="EVENT", all.x = T,all.y = T)
BiggerSeed <- merge(BiggerSeed,Score3,by="EVENT", all.x = T,all.y = T)
BiggerSeed <- merge(BiggerSeed,Score4,by="EVENT", all.x = T,all.y = T)
BiggerSeed <- merge(BiggerSeed,Score5,by="EVENT", all.x = T,all.y = T)
BiggerSeed <- merge(BiggerSeed,Score6,by="EVENT", all.x = T,all.y = T)
BiggerSeed <- merge(BiggerSeed,Score7,by="EVENT", all.x = T,all.y = T)
BiggerSeed <- subset(BiggerSeed, select = c(1,2,4,6,8,10,12,14,3,5,7,9,11,13,15))

BiggerSeed[is.na(BiggerSeed)] = 1000
BiggerSeed$SCORE <- apply(BiggerSeed[,c(2:8)], 1, FUN=min)
BiggerSeed$seed <- colnames(BiggerSeed[,c(2:8)])[apply(BiggerSeed[,c(2:8)], 1, FUN=which.min)] 

rownames(BiggerSeed) = NULL
BiggerSeed = subset(BiggerSeed,select=c(1,16,17))
BiggerSeed <- BiggerSeed[order(BiggerSeed$SCORE),]
BiggerSeed = subset(BiggerSeed,SCORE < 999)
#write.csv(BiggerSeed,"BiggerSeed.csv")

#merge elife and seeds and their seed scores----
elife_seed = merge(elife,BiggerSeed,by="EVENT")
#write.csv(elife_seed,"norm-PSI-and-best-Seed.csv")

#Filtering Seed Score
elife_scorefiltered <- subset(elife_seed,SCORE <=elifeSeedScore)
```


Find A` (what sig events from Pengda overlap with D)
```{r}
overlap_A <- merge(pengda_WTvT200M_filtered,overlap_D,by ="EVENT")
```


Find B` (what sig events from Elife overlap with D)
```{r}
overlap_B <- merge(elife_scorefiltered, overlap_D, by = "EVENT")
```

Find C (what sig events are shared with by A` and B`)
```{r}
overlap_C <- merge(overlap_A,overlap_B, by = "EVENT")
```


here I calculate the hypergeometric distribution
```{r}
q = as.numeric(dim(overlap_C)[1])
m = as.numeric(dim(overlap_A)[1])
n = as.numeric(dim(overlap_D)[1] -m)
k = as.numeric(dim(overlap_B)[1])

phyper(q =q,m = m,n = n, k =k,lower.tail = F)

```


```{r}
#pheatmap----
anno <- data.frame(SEED=elife_seed$seed,SCORE=elife_seed$SCORE,EVENT =elife_seed$Event)

rownames(elife_seed) <- elife_seed$EVENT
rownames(anno) <-  elife_seed$EVENT

cat_df = data.frame("CellStage" = c("G1-S","S","S-G2","G2-M","M-G1","M-G1","G1","G1-S","S-G2","G2-M",
                                    "M-G1","M-G1","G1","G1-S"))
rownames(cat_df) = colnames(elife_seed[4:17])

elife_seed <- elife_seed[order(elife_seed$seed,elife_seed$SCORE),]

elife_seed_scoreunder3 <- subset(elife_seed,SCORE <=elifeSeedScore)

pheatmap(elife_seed[4:17], show_rownames=F,cluster_cols= F,cluster_rows = F,scale = 'row',
         annotation_row = anno,annotation_col = cat_df, cellwidth = 10,color=colorRampPalette(c("red", "white", "blue"))(150),
         border_color = NA)
```
Venn Diagram and Other Viz
```{r}
install.packages("BioVenn")
library(BioVenn)
Pengda <- as.character(overlap_A$EVENT)
Elife <- as.character(overlap_B$EVENT)
Empty <- NULL

A_B <- as.data.frame(cbind(overlap_A$events.x,overlap_B$Event.x))
A_B <- data.frame(x=unlist(A_B))

q <- draw.venn(Pengda,Elife,Empty,title = "AS EVENTS",subtitle = " ",xtitle = "PENGDA",
          ytitle = "ELIFE",y_c = "blue",output = "pdf",filename = "Venn Diagram",
          yt_s = 2,xt_s = 2,nr_s = 2)


C <- ggplot(overlap_C, aes(x=events.x))+
  geom_bar(stat="count", width=0.7, fill="steelblue")+
  theme_minimal()

ggplot(overlap_A, aes(x=events.x))+
  geom_bar(stat="count", width=0.7, fill="red")+
  theme_minimal()

ggplot(overlap_B, aes(x=Event.x))+
  geom_bar(stat="count", width=0.7, fill="green")+
  theme_minimal()

A <- ggplot(overlap_D, aes(x=events))+
  geom_bar(stat="count", width=0.7, fill="green")+
  theme_minimal()

B <- ggplot(A_B, aes(x=x))+
  geom_bar(stat="count", width=0.7, fill="green")+
  theme_minimal()


gg <- ggarrange(A, B,C, 
          labels = c("A", "B","C"),
          ncol = 3, nrow = 1)


pp <- data.frame(Events = c("A3SS","A5SS","MXE","RI","SE"),
                    percent =c(sum(overlap_C$events.x=="A3SS")/sum(A_B$x=="A3SS")*100,
                               sum(overlap_C$events.x=="A5SS")/sum(A_B$x=="A5SS")*100,
                               sum(overlap_C$events.x=="MXE")/sum(A_B$x=="MXE")*100,
                               sum(overlap_C$events.x=="RI")/sum(A_B$x=="RI")*100,
                               sum(overlap_C$events.x=="SE")/sum(A_B$x=="SE")*100))

```


Events that overlap so I can do GO Analysis
```{r}
overlapping_genes <- subset(overlap_C,select = c(1))
colnames(overlapping_genes) <- c("GENES")
overlapping_genes <- data.frame(do.call('rbind', strsplit(as.character(overlapping_genes$GENES),'_',fixed=TRUE)))
overlapping_genes <- subset(overlapping_genes,select = c(1))
colnames(overlapping_genes) <- c("GENES")
overlapping_genes <- unique(overlapping_genes)


ah <- AnnotationHub()
orgs <- subset(ah, ah$rdataclass == "OrgDb")
orgdb <- query(orgs, "Homo sapiens")[[1]]
k = as.character(overlapping_genes$GENES)
go <- AnnotationDbi::select(orgdb, k, "GO", "SYMBOL")
go1 <- go[go$ONTOLOGY == "BP",] # biological processes
go1 <- subset(go1,select = c(1,2))
go1 <-unique(go1)
go2 <- AnnotationDbi::select(GO.db, go1$GO, c("TERM","DEFINITION"), "GOID")
counting_BP <- as.data.frame(count(go2, TERM))
counting_BP <- counting_BP[order(-counting_BP$n),]
head(counting_BP,10)

go3 <- go[go$ONTOLOGY == "MF",] # Molecular Function
go3 <- subset(go3,select = c(1,2))
go3 <-unique(go)
go4 <- AnnotationDbi::select(GO.db, go3$GO, c("TERM","DEFINITION"), "GOID")
counting_MF <- as.data.frame(count(go4, TERM))
counting_MF <- counting_MF[order(-counting_MF$n),]
head(counting_MF,10)

 


```



